### 2016-08-31 README.Rmd
udpate readme with build status

```{r env, echo=FALSE}
opts_chunk$set(comment=NA)
```

@@

```{r installgh, eval = FALSE}
biocLite("lgato/MSnbase")
```

@@

>>>>

```{r env, echo=FALSE}
knitr::opts_chunk$set(comment=NA)
```

@@

```{r installgh, eval = FALSE}
biocLite("lgatto/MSnbase")
```

## Build status

This repository, `master` branch
[![Build Status](https://travis-ci.org/lgatto/MSnbase.svg?branch=master)](https://travis-ci.org/lgatto/MSnbase)

@@

## Contributing

Contributions to the package are more than welcome. If you want to
contribute to this package, you should follow the same conventions as
the rest of the functions whenever it makes sense to do so. Feel free
to get in touch (preferable opening a
[github issue](https://github.com/lgatto/MSnbase/issues/)) to discuss
any suggestions. The
[`MSnbase` development vignette](http://bioconductor.org/packages/devel/bioc/vignettes/MSnbase/inst/doc/MSnbase-development.pdf)
gives some background on the class infrastructure.

Please note that this project is released with a
[Contributor Code of Conduct](https://github.com/lgatto/MSnbase/blob/master/CONDUCT.md). By
participating in this project you agree to abide by its terms.
